---
title: "Getting Started with binomial"
author: "Jue Luo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

1. bin_choose() calculates the number of combinations in which k successes can occur in n trials.

```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0) 
bin_choose(5, 1:3)
```

2. bin_probability() calculates the probability of a binomial variable.

```{r}
# probability of getting 2 successes in 5 trials (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
# probabilities of getting 2 or less successes in 5 trials # (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
 # 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
```

3. bin_distribution() calculates the distribution for a binomial variable.
    Method plot.bindis() is to graphs a barplot to display the probability histogram of a binomial distribution object "bindis".
```{r}
bin_distribution(trials = 5, prob = 0.5)
dis1 <- bin_distribution(trials = 5, prob = 0.5) 
plot(dis1)
```

4. bin_cumulative() calculates the cumulative probability of a binomial variable
    Method plot.bincum() is to graphs the cumulative distribution in ab object "bincum".
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

5. bin_variable() creates an object of class "binvar".
    Method print.binvar() is to nicely print the content of an object "binvar".
    Method summary.binvar() and print.summary.binvar() is to get a full summary description of an object "binvar".
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```


6. Functions of measures contain main functions for each of the summary measures including bin_mean(), bin_variance(),
  bin_mode(), bin_skewness(), bin_kurtosis()
  
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```


